Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2021-06-24 doc/manuscript/ESSDmanuscript.Rmd
Update ESSDmanuscript.Rmd
@mawilliams99 ,  in line 251 I'm trying (with my inadequate R skills!) to exclude rows for which Motivation = "housekeeping" from the table, but this is not working.  If this is fast for you, it would be great if you could help.

```{r table_ForCchanges, eval = TRUE, echo=FALSE, warning=FALSE}
library (readr)
urlfile="https://raw.githubusercontent.com/forc-db/ForC/master/database_management_records/record_of_changes.csv"
record_of_changes<-read_csv(url(urlfile))
names(record_of_changes) <- stringr::str_replace_all(names(record_of_changes), "\\.", " ")
record_of_changes <- record_of_changes[c(1:5)] #include all fields but date of change
record_of_changes[is.na(record_of_changes)]<- "" #replace NAs with blanks

>>>>

```{r table_ForCchanges, eval = TRUE, echo=FALSE, warning=FALSE, message = FALSE}
library (readr)
urlfile="https://raw.githubusercontent.com/forc-db/ForC/master/database_management_records/record_of_changes.csv"
record_of_changes <-read_csv(url(urlfile))
names(record_of_changes) <- stringr::str_replace_all(names(record_of_changes), "\\.", " ")
record_of_changes <- record_of_changes[c(1:5)] #include all fields but date of change
#record_of_changes<- record_of_changes[which(!grep("housekeeping",record_of_changes$Motivation)) , c(1:5)]  #trying to exclude rows for which Motivation = "housekeeping", but this is not working
record_of_changes[is.na(record_of_changes)]<- "" #replace NAs with blanks
